Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-23 paper.tex
final fixes

\myabstract{
Due to the diversity of fuel cycle simulator modeling assumptions, direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study that
is perhaps the most complete published comparisons performed.  Despite this,
various results from the simulators were often significantly different due to
inconsistency in modeling decisions involving reprocessing strategies,
refueling behavior, reactor end-of-life handling, etc.  This work identifies
and quantifies the effects of selected modeling choices that may sometimes be
taken for granted in the fuel cycle modeling domain.  Four scenarios are
compared using combinations of either fleet-based or individual reactors with
either monthly or quarterly (3-month) time steps.  The scenarios approximate a
transition from the current once-through light water reactor (LWR) fleet to a
full sodium fast reactor (SFR) fuel cycle The Cyclus fuel cycle simulator's
plug-in facility capability along with its market-like dynamic material
routing allow it to be used as a level playing field for comparing the
scenarios.  When under supply-constraint pressure, the four cases exhibit
noticeably different behavior.  Fleet-based modeling is more efficient in
supply-constrained environments at the expense of losing insight on issues
such as realistically suboptimal fuel distribution and challenges in reactor
refueling cycle staggering.  Finer-grained time steps also enable more
efficient material use in supply-constrained environments.  Large simulations
with fleet-based reactors run much more quickly than their individual reactor
counterparts.  Gaining a better understanding of how these and other modeling
choices affect fuel cycle dynamics will enable making more deliberate
decisions with respect to trade-offs such as computational investment vs.
realism.
}

@@

TODO: thank ross maybe for vision-sourced inspiration about modeling effects

>>>>

\myabstract{
Due to the diversity of fuel cycle simulator modeling assumptions, direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study that
is perhaps the most complete published comparison performed.  Despite this,
various results from the simulators were often significantly different due to
inconsistency in modeling decisions involving reprocessing strategies,
refueling behavior, reactor end-of-life handling, etc.  This work identifies
and quantifies the effects of selected modeling choices that may sometimes be
taken for granted in the fuel cycle modeling domain.  Four scenarios are
compared using combinations of either fleet-based or individually modeled reactors with
either monthly or quarterly (3-month) time steps.  The scenarios approximate a
transition from the current U.S. once-through light water reactor (LWR) fleet to a
full sodium fast reactor (SFR) fuel cycle. The Cyclus fuel cycle simulator's
plug-in facility capability along with its market-like dynamic material
routing allow it to be used as a level playing field for comparing the
scenarios.  When under supply-constraint pressure, the four cases exhibit
noticeably different behavior.  Fleet-based modeling is more efficient in
supply-constrained environments at the expense of losing insight on issues
such as realistically suboptimal fuel distribution and challenges in reactor
refueling cycle staggering.  Finer-grained time steps also enable more
efficient material use in supply-constrained environments.  Large simulations
with fleet-based reactors run much more quickly than their individual reactor
counterparts.  Gaining a better understanding of how these and other modeling
choices affect fuel cycle dynamics will enable making more deliberate
decisions with respect to trade-offs such as computational investment vs.
realism.
}

@@
